Simulation_Study

### 2022-03-06 Simulation_Study.Rmd
Vary Sample Size with Same Block Length

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sd) 
  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

@@

  # Variance Stuff that isn't working
  # 95 % Confidence Interval for Variance -> Lower bound: (n - 1) * sample_variance(X_t) / chisq(.025, n - 1)
  # Upper bound: (n - 1) * sample_variance(X_t) / chisq(.975, n - 1)
  # sample_variance(X_t) = se^2 * n

@@

```{r functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)
nmcount = 0
mvcount = 0
nmchicount = 0
mvchicount = 0

sim <- replicate(100, do1rep(100, 0.1, 0.1, 10, m1))

my_summary <- function(x)
{
  c(rowMeans(x), sd(x[1,]))
}
my_summary(sim)
print(sim)

#Counts how many times the true statistic was found in the interval

@@

>>>>

do1rep <- function(n, theta, sd, l, statistic) {
  x <- arima.sim(list(ar = theta), n = n, sd = sd)

  # sd is the standard deviation of the noise -> true_variance(X_t) = sd^2/(1 - theta^2)

@@

@@

```{r functions, echo = False}
options(max.print = 1000000)
ar1 <- function(x) cor(x[-1], x[-length(x)])
m1 <- function(x) mean(x)

my_summary <- function(x)
{
  rm = rowMeans(x)
  c(rm, sd(x[1,]), rm[2] - sd(x[1,]), rm[6] - sd(x[1,]), (rm[2] - sd(x[1,])) / sd(x[1,]), (rm[6] - sd(x[1,])) / sd(x[1,]))
}

@@

```{r functions, echo = False}
sim <- replicate(100, do1rep(100, 0.5, 0.1, 10, m1))

n_100 <- my_summary(sim)

sim <- replicate(100, do1rep(200, 0.5, 0.1, 10, m1))

n_200 <- my_summary(sim)

sim <- replicate(100, do1rep(300, 0.5, 0.1, 10, m1))

n_300 <- my_summary(sim)

sim <- replicate(100, do1rep(400, 0.5, 0.1, 10, m1))

n_400 <- my_summary(sim)

sim <- replicate(100, do1rep(500, 0.5, 0.1, 10, m1))

n_500 <- my_summary(sim)

sim <- replicate(100, do1rep(600, 0.5, 0.1, 10, m1))

n_600 <- my_summary(sim)

sim <- replicate(100, do1rep(700, 0.5, 0.1, 10, m1))

n_700 <- my_summary(sim)

sim <- replicate(100, do1rep(800, 0.5, 0.1, 10, m1))

n_800 <- my_summary(sim)

sim <- replicate(100, do1rep(900, 0.5, 0.1, 10, m1))

n_900 <- my_summary(sim)

sim <- replicate(100, do1rep(1000, 0.5, 0.1, 10, m1))

n_1000 <- my_summary(sim)

n_constant_l.data <- data.frame(
   n = c(100, 200, 300, 400, 500, 600, 700, 800, 900, 1000),
   ar = c(0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5, 0.5),
   sigma = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1),
   l = c(10, 10, 10, 10, 10, 10, 10, 10, 10, 10),
   mean = c(n_100[1], n_200[1], n_300[1], n_400[1], n_500[1], n_600[1], n_700[1], n_800[1], n_900[1], n_1000[1]), 
   nm_se = c(n_100[2], n_200[2], n_300[2], n_400[2], n_500[2], n_600[2], n_700[2], n_800[2], n_900[2], n_1000[2]),
   nm_lower = c(n_100[3], n_200[3], n_300[3], n_400[3], n_500[3], n_600[3], n_700[3], n_800[3], n_900[3], n_1000[3]), 
   nm_upper = c(n_100[4], n_200[4], n_300[4], n_400[4], n_500[4], n_600[4], n_700[4], n_800[4], n_900[4], n_1000[4]),
   nm_success = c(n_100[5], n_200[5], n_300[5], n_400[5], n_500[5], n_600[5], n_700[5], n_800[5], n_900[5], n_1000[5]),
   mv_se = c(n_100[6], n_200[6], n_300[6], n_400[6], n_500[6], n_600[6], n_700[6], n_800[6], n_900[6], n_1000[6]),
   mv_lower = c(n_100[7], n_200[7], n_300[7], n_400[7], n_500[7], n_600[7], n_700[7], n_800[7], n_900[7], n_1000[7]), 
   mv_upper = c(n_100[8], n_200[8], n_300[8], n_400[8], n_500[8], n_600[8], n_700[8], n_800[8], n_900[8], n_1000[8]),
   mv_success = c(n_100[9], n_200[9], n_300[9], n_400[9], n_500[9], n_600[9], n_700[9], n_800[9], n_900[9], n_1000[9]),
   true_se = c(n_100[10], n_200[10], n_300[10], n_400[10], n_500[10], n_600[10], n_700[10], n_800[10], n_900[10], n_1000[10]),
   nm_diff = c(n_100[11], n_200[11], n_300[11], n_400[11], n_500[11], n_600[11], n_700[11], n_800[11], n_900[11], n_1000[11]),
   mv_diff = c(n_100[12], n_200[12], n_300[12], n_400[12], n_500[12], n_600[12], n_700[12], n_800[12], n_900[12], n_1000[12]),
   nm_percent_change = c(n_100[13], n_200[13], n_300[13], n_400[13], n_500[13], n_600[13], n_700[13], n_800[13], n_900[13], n_1000[13]),
   mv_percent_change = c(n_100[14], n_200[14], n_300[14], n_400[14], n_500[14], n_600[14], n_700[14], n_800[14], n_900[14], n_1000[14])
)
print(n_constant_l.data)
```
